An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-28 VLDB2026/main.tex
Update main.tex

	{\color{blue}{
		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design. For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced. Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors. FAISS-IVF, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.

>>>>

	{\color{blue}{
		Algorithms that are highly sensitive to attribute distribution tend to rely passively on the statistical characteristics of the attributes in their design. For instance, graph-based indexing methods like FilteredVamana and NHQ are prone to degraded connectivity or distorted structures under power-law distributions, where label frequencies are highly imbalanced. Similarly, VBASE, which employs a post-filtering strategy, shows efficiency that directly correlates with attribute selectivity—the more selective the filter, the more computational resources are wasted on retrieving irrelevant vectors. Faiss, which searches within the nearest clusters, may also suffer when relevant data points are unevenly distributed across clusters due to attribute skew, potentially excluding qualified results.
